Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-31 awipev-CO2.Rmd
pH at various depths now works

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("hms")
library("ragg")
knitr::opts_chunk$set(echo = TRUE)

@@

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                       date = d_hour$date,
                       month = month(d_hour$datetime))
```

@@

# pH seaFET Final
# add despike with n=2 k = 5762 to the final ph corrected data
# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
d_all <- d_all %>%
  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
  dplyr::mutate(pHint_tot_sf_9m = ifelse(pressure_insitu_ctd > 8, pHint_tot_sf, NA),
                pHint_tot_sf_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA))

@@

p <- ggplot(d_all, aes(x=datetime, y= pHint_tot_sf_9m))+
  geom_point(size=1, alpha=0.5, na.rm=TRUE)
p

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_6m, pHint_tot_sf_9m)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_6m", label = "pHT 6m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

#RANGE of pH
d_all<- d_all%>%
  dplyr::mutate(year = year(datetime))
range <- d_all %>%
  group_by(date=as.Date(datetime), 
           month=month(datetime, label=TRUE), 
           year=year(datetime)) %>%
  summarize(pH_range_9m = max(pHint_tot_sf_9m) - min(pHint_tot_sf_9m),
            pH_range_6m = max(pHint_tot_sf_6m) - min(pHint_tot_sf_6m))

quant <- quantile(range$pH_range_9m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
print(quant)
quant <- quantile(range$pH_range_6m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
print(quant)

#Per month
range_month <-
  range %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month6m = mean(pH_range_6m, na.rm=TRUE),
            pH_range_month_9m = mean(pH_range_9m, na.rm=TRUE)) %>%
  ungroup()

size_point <- 0.4 #size of data points
p <- range_month %>%
  pivot_longer(-Month, names_to = "depth", values_to = "pH_range") %>%
  ggplot() +
  geom_violin(aes(x = as.factor(Month), y = pH_range), fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(p) # plot_range_sf
#ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
```

@@

```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(temp_mix_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            temp_ctd_1m_max =round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_max =round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_max =round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_max =round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_max =round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_11m_max =round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
            temp_fb_min =round( min(temp_fb, na.rm=TRUE), digits = 2),
            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            sal_ctd_1m_max =round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_max =round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_max =round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_max =round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_max =round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
kable(range_month, caption ="")
```

>>>>

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("hms")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")

knitr::opts_chunk$set(echo = TRUE)

@@

ggplotRegression <- function(fit){
ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}

#################### MySkim
# myskim <- skim_with(numeric = sfl(min = ~min(., na.rm = TRUE),
#                                   max = ~max(., na.rm = TRUE)))
```

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate( # create new variable depth
    depth = ifelse(
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                       date = d_hour$date,
                       month = month(d_hour$datetime))
```

@@

# pH seaFET Final
# add despike with n=2 k = 5762 to the final ph corrected data
# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
d_all <- d_all %>%
  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA)
  )

@@

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_7m, pHint_tot_sf_9m)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-2, 2)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# pH by depth
# d_all<- d_all%>%
#   dplyr::mutate(year = year(datetime))

#Per month
range <- d_all %>%
  dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
            pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
            pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
  ungroup()
print(kable(range, digits = 2))
```
The range is significantly larger during some months when the data deeper than 9 m are considered. It seems therefore better to stick pH_çm, that is pH deeper than 8 m.

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
kable(range_month, caption = "")
```
